---
output: github_document
---

# ggfia

`ggfia` provides easy to use functions to display FIA plots with `ggplot2`.
`ggfia` is currently in development, with some ideas for functionality given
below.

- Compose an FIA plot resembling the Bechtold and Patterson (2005) diagram

```{r}
library(ggfia)
library(ggplot2)

plot_coord <- data.frame(
  x0 = 0, y0 = 0
)

ggplot(plot_coord, aes(x0 = x0, y0 = y0)) +
  geom_macroplot(linetype = "dashed") +
  geom_midplot() +
  geom_microplot() +
  geom_subp_center() +
  coord_equal()
```

- Display only the midplot

Note that we use the term "midplot" to avoid conflating with "subplot", which
refers to a relative plot position index.

```
ggplot() +
  geom_midplot()
```

- Display multiple plot diagrams

```{r}
multi_plot_coords <- expand.grid(
  x0 = seq(0, 1000, by = 500),
  y0 = seq(0, 1000, by = 500)
)

ggplot(multi_plot_coords, aes(x0 = x0, y0 = y0)) +
  geom_macroplot(linetype = "dashed") +
  geom_midplot() +
  coord_equal()
```

- Apply colors and facets

```{r}
multi_plot_coords$my_group <- factor(1:9)

ggplot(multi_plot_coords) +
  geom_macroplot(aes(x0 = x0, y0 = y0, color = my_group)) +
  facet_wrap(~my_group) +
  coord_equal()
```

- Display other geoms over the plot
```{r}
pts <- data.frame(x = runif(10, -20, 20), y = runif(10, -20, 20))

ggplot() +
  geom_midplot(aes(x0 = x0, y0 = y0), data = plot_coord) +
  geom_point(aes(x = x, y = y), data = pts) +
  coord_equal()
```